

% ===============================================
\section{Education}{}

\begin{tabularx}{\textwidth}{l X}
    %------------------------------------------------	
    \textbf{PhD.} & University of Tehran, Mechanical Engineering, Hydraulic Machinery \\
    2012 -- 2018 & Thesis: Uncertainty quantification of turbulent flows in hydraulic machinery \\
    & Supervisors: Prof. Mehrdad Raisee, Prof. Michel Cervantes, Prof. Ahmad Nourbakhsh\\
    & The thesis investigates the impact of operational and geometrical uncertainties on the performance of hydraulic machinery, extending uncertainty quantification (UQ) to this critical field using polynomial chaos expansion (PCE). To address the high computational costs of traditional UQ methods, I developed efficient techniques such as compressed sensing and multifidelity $\ell_1$ minimization, validated through both analytical and CFD problems. Real-world case studies demonstrate that combined operational and geometrical uncertainties significantly influence the flow and performance of hydraulic pumps. This work advances UQ methods, contributing to more robust and reliable hydraulic machinery design.\\
    % & See Appendix~\ref{sec:PhD} for the PhD diploma.\\
    \multicolumn{2}{c}{} \\
    %------------------------------------------------
    \textbf{MSc.} & University of Tehran, Mechanical Engineering, Energy Conversion \\
    2010 -- 2012 & Thesis: Computation of steady and pulsating turbulent flow through a straight asymmetric diffuser with moderate adverse pressure gradient \\
    & Supervisors: Prof. Mehrdad Raisee, Prof. Michel Cervantes\\
    
    \multicolumn{2}{c}{} \\
    %------------------------------------------------
    \textbf{BSc.} & University of Tehran, Mechanical Engineering \\
    2006 -- 2010 & Thesis: Large eddy simulation of stall development around airfoils \\
    %------------------------------------------------
\end{tabularx}
% ===============================================

