% ===============================================
\section{Current Position}

\begin{tabularx}{\textwidth}{l X}
    \textbf{Associate Professor} & Linköping University \\
    2025 -- present & Division of Applied Thermodynamics and Fluid Mechanics, Department of Management and Engineering. My research focuses on combining data-driven methods and artificial intelligence with Computational Fluid Dynamics (CFD) to develop efficient and reliable methods for simulation, model reduction, control, and uncertainty quantification of fluid flows. 

    I have also received my Docent title in Fluid Mechanics at Linköping University in February 2026. \\

    \\
\end{tabularx}
% ===============================================


% ===============================================
\section{Previous Appointments}

\begin{tabularx}{\textwidth}{l X}

    %------------------------------------------------
    \textbf{Researcher} & Employed by \href{https://chalmersindustriteknik.se/en/}{Chalmers Industriteknik (CIT)}, conducting research on \\
    2023 -- 2025 & the application of artificial intelligence and machine learning in computational fluid dynamics. During my time at CIT, I was hired by Chalmers University of Technology for a project on ``Artificial Intelligence in Fluid Dynamics for Improving the Lifetime of Hydraulic Turbines''.
    \\
    \multicolumn{2}{c}{} \\
    %------------------------------------------------

    %------------------------------------------------
    \textbf{Postdoc} & Chalmers University of Technology \\
    2019 -- 2023 & Project: New operating procedures of hydropower for a sustainable energy system.
    During my postdoctoral position, my research focused on developing advanced numerical methods in OpenFOAM to simulate the transient operations of hydraulic turbines. I also expanded my expertise in data-driven and machine-learning approaches, particularly in the field of reduced-order modeling, such as Proper Orthogonal Decomposition (POD) and Dynamic Mode Decomposition (DMD).
    The research resulted in several publications in high-impact, peer-reviewed journals and an open-source software package for simulating hydraulic turbine transients, which is being utilized by Vattenfall, a leading energy company in Sweden. \\
    \multicolumn{2}{c}{} \\
    %------------------------------------------------

    %------------------------------------------------
    \textbf{Lecturer} & University of Science and Culture, Tehran, Iran \\
    2018 -- 2019 & Taught ``Introduction to Turbomachinery'' at the undergraduate level \\
    %------------------------------------------------

\end{tabularx}
% ===============================================
